Expanding tidy data principles to facilitate missing data exploration, visualization and assessment of imputations

### 2020-04-05 paper/tidy-missing-data-paper.Rmd
added a note on this section to work on
minor additions

To explore missing data there needs to be a robust representation of missing
values that integrates into analysis pipelines. This means a data structure that is easily transported, and not a special class reliant on attributes that can be lost in analysis. The $B$ matrix, where 0 and 1
indicate not missing and missing provides a useful template, as it is very common in
missing data literature.  This matrix was used to explore missing values in
the interactive graphics library XGobi, called a "missing value
shadow", or "shadow matrix", defined as a copy of the original data with
indicator values of missingness. The values 0 and 1 can
be confusing representations of missing values - does
0 indicate an absence of observation, or the presence of a missing value? 
The shadow matrix could be interactively linked to the data.

@@

We propose a new form for tidy representation of missing data based on these ideas, based on this past research. Four features are added to the shadow matrix to facilitate analysis of missing data, illustrated in Figure \@ref(fig:shadow-matrix-progress)

@@

## track: Shadow and impute missing values {#verbs-track}

@@

@@

```{r clean-data-for-analysis, include = FALSE}
# add memoise to store the output data for this
impute_knn <- simputation::impute_knn
dat_house <- housing_cls %>%
  mutate(year = lubridate::year(date),
         # month = lubridate::month(date),
         quarter = lubridate::quarter(date)) %>%
  mutate_at(vars(car, bathroom, bedroom2), as.integer)

@@

```{r impute-knn}

>>>>

(note: section to work on this week.)

- re-arrange this paragraph around

To explore missing data there needs to be a robust representation of missing
values that integrates into analysis pipelines. This means a data structure that is easily transported, and not a special class reliant on attributes that can be lost in analysis. The $B$ matrix, where 0 and 1 indicate not missing and missing (respectively), provides a useful template, as it is very common in missing data literature.  This matrix was used to explore missing values in
the interactive graphics library XGobi, called a "missing value
shadow", or "shadow matrix", defined as a copy of the original data with
indicator values of missingness. The shadow matrix could be interactively linked to the data.

There are some limitations to the shadow matrix, however. Namely, the values 0 and 1 can be confusing representations of missing values - does
0 indicate an absence of observation, or the presence of a missing value?

@@

We propose a new form for tidy representation of missing data based on these ideas from past research. Four features are added to the shadow matrix to facilitate analysis of missing data, illustrated in Figure \@ref(fig:shadow-matrix-progress)

@@

### track: Shadow and impute missing values {#verbs-track}

@@

(note: next section to work on)

@@

```{r clean-data-for-analysis, include = FALSE, cache = TRUE}
# add memoise to store the output data for this
impute_knn <- simputation::impute_knn
dat_house <- housing_cls %>%
  mutate(year = lubridate::year(date),
         # month = lubridate::month(date),
         quarter = lubridate::quarter(date)) %>%
  mutate_at(vars(car, bathroom, bedroom2), as.integer)

@@

```{r impute-knn, cache = TRUE}
